...

### 2024-09-16 draft.tex
Add Description

\bigskip
\noindent\textbf{Description:}\\
In your thesis consider the question of whether it is possible to equip graphs describing digitized images with a compatible
topology in the sense that for any part of the image the connectivity of the induced subgraph matches the topological connectivity.
Base your thesis on the article ``\textit{D. Nogly, M. Schladt. Digital Topology on graphs. Computer
vision and image understanding, Vol. 63(No. 2):\ 394\ ---\ 396}''.

>>>>

\bigskip
\noindent\textbf{Description:}\\
In your thesis consider the question of whether it is possible to equip graphs describing digital images with a compatible
topology in the sense that for any part of the image the connectivity of the induced subgraph matches the topological connectivity.
Base your thesis on the article ``\textit{D. Nogly, M. Schladt. Digital Topology on graphs. Computer
vision and image understanding, Vol. 63(No. 2):\ 394\ ---\ 396}''.
